% includes/personal_letter_drift.tex

 \documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
% eller modern:
%\usepackage[utf8]{luainputenc}
...
\begin{document}

\section*{Personal Letter}

Dear Hiring Manager,

I am writing to express my interest in the system engineer position within IT operations and DevOps. With a broad background in software development, infrastructure, and cybersecurity, I bring a strong combination of practical experience and a continuous drive to work hands-on with secure and reliable systems.

Throughout my career, I have held roles in backend development, system integration, and operations across both private and public sector projects. This diverse experience has given me transferable skills in automation, troubleshooting, CI/CD pipelines, and infrastructure as code. I am particularly passionate about creating robust, scalable environments where availability, security, and clarity are key.

Recently, I have deepened my focus on cybersecurity and ethical hacking, earning certifications such as Microsoft Azure Fundamentals (AZ-900), and completing practical training in ethical hacking (Udacity and FreeCodeCamp). I combine this knowledge with daily practice in infrastructure monitoring, container orchestration, and automation using tools like Terraform, Azure DevOps, and Kubernetes.

I am especially drawn to this role because it allows me to contribute to socially meaningful infrastructure with high security and reliability demands, while remaining close to the systems and people who keep them running. I value public trust and transparency — and I believe my background aligns well with the technical and ethical responsibilities of this position.

Thank you for considering my application. I would welcome the opportunity to discuss how I can support your team with practical experience, technical curiosity, and a calm, structured presence in operational work.

Sincerely,\\
Rickard Åberg



\end{document}


