\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[swedish]{babel}
\usepackage{geometry}
\geometry{margin=2.5cm}
\usepackage{parskip}

\signature{Rickard Åberg}
\address{Malmö \\ rickard.aaberg@icloud.com \\ 0709 43 14 01}
\date{\today}

\begin{document}

\begin{letter}{ \\ \\ }

\opening{Hi ,}
Dear Hiring Manager,
I am writing to express my strong interest in the position of Backend Java Developer at Verisure Innovation AB. With a Master’s degree in Computer Science and over 15 years of professional experience in backend development, cloud, and DevOps, I am eager to contribute to your mission of building innovative security solutions that make the world a safer place.
Throughout my career, I have worked extensively with Java, Spring Boot, and enterprise systems, developing solutions for telecom, finance, and large-scale integration projects. At Bouvet and Teleca OSS, I delivered critical backend and integration platforms for clients such as Telenor, Tre (Hi3G), IKEA IT, and Nordea. My work has combined backend development with DevOps practices, CI/CD pipelines, and cloud technologies (Azure, Kubernetes, Docker).
Beyond technical skills, I bring a senior mindset: structured, calm, and solution-oriented, even in high-pressure situations. 

I enjoy working in agile teams and believe that knowledge-sharing and collaboration are essential for long-term success. 
As an ICC/EMCC certified coach and experienced Toastmasters speaker, I naturally foster teamwork and create an environment where 
colleagues can thrive together.
I am particularly drawn to Verisure because of your commitment to security, innovation, and collaborative team culture. 

I see a strong alignment between your values and my own motivation to build reliable backend systems that have a tangible 
impact on people’s safety and everyday lives.
I would welcome the opportunity to discuss how my background in backend engineering, DevOps, and security can contribute to Verisure’s 
continued growth and innovation. Thank you for considering my application, and I look forward to the possibility of joining your team.


\closing{Sincerely,}

\end{letter}
\end{document}
