\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{lmodern}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.2}

\signature{Rickard Åberg}
\address{Bodekullsgatan 34B \\ 214 40 Malmö \\ +46 709 43 14 01 \\ rickard.aaberg@icloud.com}
\date{\today}

\begin{document}

\begin{letter}{Sandvik Rock Processing \\
Hyllie Boulevard 53 \\
215 32 Malmö}

\opening{Dear Anders Hovén,}

I am writing to express my strong interest in the position of \textbf{Senior Java Developer} at Sandvik Rock Processing (Job ID: R0078208). With a Master’s degree in Computer Science and extensive experience in Java, Spring Framework, and cloud-based microservice architectures, I am eager to contribute my skills to your Digital Solutions team and support Sandvik’s mission of driving digital transformation in the manufacturing industry. 

Over the past years, I have worked in backend development projects where I designed and implemented robust microservices, deployed as Docker containers and orchestrated with Kubernetes on Azure. I am well-versed in building RESTful APIs on Linux-based systems, together with database solutions that ensure high code quality through test automation, mocking strategies, and agile delivery practices. My hands-on approach and curiosity have often led me to expand into frontend and mobile domains, where I have explored React.js and TypeScript as well as integrations with iOS and Android platforms.  

Beyond my technical expertise, I bring strong collaboration skills and a genuine passion for problem-solving. Having led and participated in agile teams, I thrive in environments where knowledge sharing and collective responsibility are key. I value open communication and believe that diverse perspectives create stronger solutions. At Sandvik, I see a perfect match between my professional profile and your culture of innovation, inclusivity, and customer-centric product development.  

I would welcome the opportunity to discuss how my experience can contribute to Sandvik’s digital offering and long-term success. Thank you for considering my application. I look forward to the possibility of joining your team in Malmö and to making a tangible impact on future solutions.  

\closing{Sincerely,}

\end{letter}
\end{document}
