
\section{Developer experiences etc}


\section{Todo}
\cventry{2025 VT -- }{Jhipster}{https://www.jhipster.tech/}{Remote}{Java Jascript}{Open Source}

\cventry{2025 VT -- }{Fia Med Knuff}{https://github.com/kizouker/Fia_med_knuff.git}{Remote}{Java Jascript .Net core RabbitMQ}{Open Source}
\cventry{2025}{radioforum.se}{Upgrade of phpbb}{Git, branches, releasemanagement}{}{}
\cventry{2025}{ReDI School of Digital Integration}{Cloud Computing and Azure Security}{Hands-on labs from Microsoft 12+}{}{}
\cventry{2024 VT -- }{Zetkin Foundation}{https://github.com/zetkin/app.zetkin.org/}{Malmö}{React Typescript}{React Typescript Front-End Open Source}
\cventry{2023 VT --  }{Open Trip Planner (OTP)}{https://www.opentripplanner.org/}{Malmö}{Java}{OWASP plugin, Java21, GraphQL, python, open source}
\cventry{2022 HT  }{Hot Yoga Malmö}{hotyogamalmo.se}{Malmö}{Wordpress}{Wordpress, plugins, php, loopia}
\cventry{2021-12 -- 2022-06-01 }{ADBSafegate AB}{ADBSafegate AB}{Malmö}{Fullstack Developer}{Angular, typescript, Azure, Scaled Agile Framework, SAFe}
\cventry{2019-2021 }{React.JS Nanodegree}{@ Udacity}{}{}{Projects - reviewed and passed by react experts:}
\begin{itemize}
  \item  \url{https://github.com/kizouker/reactnd-project-would-you-rather-starter}
\end{itemize}
\cventry{2019-}{Therealantidepp}{Open Source}{Malmö}{}{Help people to avoid depression. Java 11 (HttpClient), Spring boot, Hibernate, RESTful API/JSON, Swagger. }

\cventry{2017-2018}{Fullstack Developer }{@ Verisure}{Malmö}{}{Java8, android, Docker/Kubernetes, wildfly, maven, jsp, javascript, jquery, bootstrap, AJAX, RESTful, mysql (Cassandra), git/gerrit, Linux/Ubuntu, IntelliJ, SonaQube, Nexus, Jenkins CI, Artifactory.}
\begin{itemize}
    \item Setup of Microservice deployment to kobol/galactica in kubernetes, myhotel 
    \item Android development for ipcaminit   
    \item Hands-on development in the GWIT/Installer Solutions, Fullstack – from db to javascript 
    \item GDPR coordinator
    Responsible for analyzing the data passing trough an application and how it relates to General Data Protection Regulation, communication with Legal, Projects and Managers. 
\end{itemize}

\cventry{HT2016 }{Community services in Stockholm}{@ SL}{}{}{Participated in the project responsible for improving processes around CM. Developing and maintaining a system in Java for sick travels. GitLab, Sonatype, Nexus, Maven, Git, JEE, Jenkins CI. }  
\cventry{2014--2015}{Java developer - Java EE, Spring, Maven, Hibernate and Linux Ubuntu.}{@ Norwegian fur retailer}{}{}{Bouvet maintains an auction web-site for a Norwegian retailer of fur materials, based on JEE, hibernate, java6. I have worked to support this the site, trouble shoot, fix bugs etc. One part has been to migrate from Redhat to Scientific Linux. }  
\cventry{2011--}{Solution Architect}{@ IKEA IT}{Helsingborg}{}{Evaluated SaaS (Software-as-a-Service, cloud computing) for a custom support system to be presented to the enterprise architecture board (EAB). The report took into account aspects such as integration issues, security, capacity, economy, legality etc.}  
\cventry{2011--}{System Integration Specialist – TIBCO - Application Lead}{@ Hi3G (TRE)}{}{Stockholm}{
Application Lead for EAI (Enterprise Application Integration) – a layer consisting of 15 adapters to systems for example Billing (Single.E.View), CRM (PeopleSoft) and so on. }
\cventry{2008-2010}{Java Developer and Project Coordinator}{@ -IKEA IT}{HBG}{During my assignment at IKEA IT in 2008, parts of the organization were focused on achieving PCI DSS compliance, although I was not directly involved in that initiative.}{} 
\cventry{2004--2012}{Java Developer and Integration specialist}{@ Telenor}{Oslo/Malmö}{}{Back-end and system integration developer Java EE and Tibco products. Delivering speed and  progress for the project which was six months late after schedule. CI-servers, cruise control – code coverage etc. 
}  