\section{Developer Experience (Support-Oriented)}

\cventry{2017--2018}{Verisure Innovation}{Senior Software Engineer}{Malmö}{Java, Android, Kubernetes}{
Contributed to internal IT tools for camera installers and support teams. Led GDPR compliance integration and worked cross-functionally with legal and infrastructure teams to ensure user data protection. Designed a deployment pipeline to improve reliability and reduce downtime for support-critical systems.
}

\cventry{2015--2016}{Länsstyrelsernas IT-enhet}{Problem Manager}{Remote}{ITIL, Incident/Problem mgmt}{
Led problem-solving across departments including Service Desk, GIS, Network and Print. Reduced critical error codes from 1400 to 50 per month. Introduced structured follow-ups, escalation workflows and architectural fixes to prevent recurring incidents.
}

\cventry{2012--2014}{IKANO Bank}{Release Manager / DevOps Coach}{Remote}{.NET, BizTalk, Jenkins}{
Managed application deployments and cross-team coordination. Acted as a liaison between operations, support and developers. Automated release processes and improved documentation, reducing support effort and handover confusion. Collaborated actively with Service Desk during handovers.
}

\cventry{2011--}{Hi3G (TRE)}{System Integration Specialist \& App Lead}{Stockholm}{TIBCO, CRM Integration}{
Owned application landscape integration for 15 systems. Supported CRM and billing platforms, with close contact with Service Desk and infrastructure. Provided 2nd-line support, coordinated incident resolution and ensured system availability during critical operations.
}

\cventry{2008--2010}{IKEA IT}{Project Coordinator \& Support Tools Rollout}{Helsingborg}{Java, PCI DSS}{
Coordinated rollout of custom IT tools to bridge in-store operations and central IT. Ensured usability and technical stability of internal support systems. Collaborated with store staff, support agents, and infrastructure teams.
}

\cventry{2004--2012}{Telenor}{Integration Specialist}{Oslo/Malmö}{Java EE, Tibco, BPM}{
Contributed to integration testing, Jira plugin development, and architecture documentation. Worked closely with business units and operations to ensure stable middleware performance. Support-focused development with emphasis on maintainability.
}
