\section{In Progress & Side Projects}

\cventry{Spring 2025 -- }{JHipster Exploration}{https://www.jhipster.tech/}{Remote}{Java, JavaScript}{Exploratory project working with JHipster to generate Spring Boot + Angular applications. Focus on microservice architecture and DevOps automation.}

\cventry{Spring 2025 -- }{Fia Med Knuff (Open Source Game)}{https://github.com/kizouker/Fia_med_knuff.git}{Remote}{Java, JavaScript, .NET Core, RabbitMQ}{Design and implementation of a microservice-based board game engine. Messaging, backend logic and web UI under development.}

\cventry{Spring 2025}{Radioforum.se}{Upgrade of phpBB forum}{Malmö}{PHP, Git, Branch Strategy, Release Management}{Modernizing legacy PHP forum. Focus on maintainability and deployment workflow.}

\cventry{2025}{ReDI School of Digital Integration}{Cloud Computing and Azure Security}{Remote}{Hands-on Labs}{12+ labs with Microsoft’s learning environment, covering Azure CLI, PowerShell, ARM templates, and cloud security concepts. Preparing for AZ-500.}

\section{Developer Experience}

\cventry{Spring 2024 -- }{Zetkin Foundation (Open Source)}{https://github.com/zetkin/app.zetkin.org/}{Malmö}{React, TypeScript}{Front-end contributions to an open-source organizing platform. UI components, TypeScript logic, Git-based collaboration.}

\cventry{2023 --  }{OpenTripPlanner Exploration (Open Source)}{https://www.opentripplanner.org/}{Malmö}{Java, Python, GraphQL}{Local deployment and customization of OTP for routing and geospatial data handling. Explored Java21 plugin integration and OWASP hardening.}

\cventry{Fall 2022}{Hot Yoga Malmö}{hotyogamalmo.se}{Malmö}{WordPress, PHP}{Website improvements, plugin integration and hosting migration using Loopia.}

\cventry{2021-12 -- 2022-06}{ADBSafegate AB}{Fullstack Developer}{Malmö}{Angular, TypeScript, Azure, SAFe}{Contributed to airfield ground lighting system UI. Developed features in Angular, managed state, and integrated with Azure services.}

\cventry{2019--2021}{React.JS Nanodegree}{Udacity by Accenture}{Remote}{React, Redux, ES6}{Completed project-based education with hands-on projects reviewed by industry experts.}
\begin{itemize}
  \item \url{https://github.com/kizouker/reactnd-project-would-you-rather-starter}
\end{itemize}

\cventry{2019--}{Therealantidepp (Open Source)}{Malmö}{Java 11, Spring Boot, REST API}{Designed and built a backend service focused on mental health. Integrated Swagger documentation and Hibernate ORM.}

\cventry{2017--2018}{Verisure Innovation}{Fullstack Developer}{Malmö}{Java8, Android, Docker, Kubernetes}{Fullstack developer for internal systems and camera installers. Led GDPR compliance integration.}
\begin{itemize}
    \item Designed microservice deployment pipeline on Kubernetes
    \item Developed Android component for camera initialization (ipcaminit)
    \item Led GDPR compliance implementation in internal apps
\end{itemize}

\cventry{Fall 2016}{Stockholm Public Transit (SL)}{Community Tech Support}{Stockholm}{Java, JEE, Maven}{Contributed to improvements in sick travel processing systems. Worked in GitLab and CI environment.}

\cventry{2014--2015}{Norwegian Fur Auction}{Bouvet (Consultant)}{Remote}{Java EE, Spring, Hibernate}{Supported and maintained auction platform. Migrated system from Redhat to Scientific Linux.}

\cventry{2011--}{IKEA IT}{Solution Architect}{Helsingborg}{SaaS, Architecture Evaluation}{Authored internal report on SaaS solution feasibility including legal, integration, and security aspects.}

\cventry{2011--}{Hi3G (TRE)}{System Integration Specialist}{Stockholm}{TIBCO, EAI, CRM Integration}{Led integration of 15 systems including billing and CRM. Application lead for middleware layer.}

\cventry{2008--2010}{IKEA IT}{Java Developer and Coordinator}{Helsingborg}{PCI DSS, Java}{Coordinated rollout of support tools. Bridged in-store operations with central IT systems.}

\cventry{2004--2012}{Telenor}{Integration Specialist}{Oslo/Malmö}{Java EE, Tibco, BPM}{Led integration tests and architectural templates. Developed Jira plugins and contributed to award-winning BPM solution.}

\cventry{2003--2004}{Ecole des Mines de Nantes}{Research Engineer}{Nantes, France}{Java, RMI, Struts}{Conducted thesis and research on event-driven components. Collaborated with researchers in Vienna.}


% \section{Todo / In progress}
% %\cventry{2025 VT -- }{Jhipster}{https://www.jhipster.tech/}{Remote}{Java Jascript}{Open Source}
% \cventry{2025 VT -- }{Fia Med Knuff}{https://github.com/kizouker/Fia_med_knuff.git}{Remote}{Java Jascript .Net core RabbitMQ}{Open Source}
% \cventry{2025}{radioforum.se}{Upgrade of phpbb}{Git, branches, releasemanagement}{}{}
% \cventry{2025}{ReDI School of Digital Integration}{Cloud Computing and Azure Security}{Hands-on labs from Microsoft 12+}{}{}


% \section{Developer experiences etc}
% \cventry{2024 VT -- }{Zetkin Foundation}{https://github.com/zetkin/app.zetkin.org/}{Malmö}{React Typescript}{React Typescript Front-End Open Source}
% \cventry{2023 VT --  }{Open Trip Planner (OTP)}{https://www.opentripplanner.org/}{Malmö}{Java}{OWASP plugin, Java21, GraphQL, python, open source}
% \cventry{2022 HT  }{Hot Yoga Malmö}{hotyogamalmo.se}{Malmö}{Wordpress}{Wordpress, plugins, php, loopia}
% \cventry{2021-12 -- 2022-06-01 }{ADBSafegate AB}{ADBSafegate AB}{Malmö}{Fullstack Developer}{Angular, typescript, Azure, Scaled Agile Framework, SAFe}
% \cventry{2019-2021 }{React.JS Nanodegree}{@ Udacity}{}{}{Projects - reviewed and passed by react experts:}
% \begin{itemize}
%   \item  \url{https://github.com/kizouker/reactnd-project-would-you-rather-starter}
% \end{itemize}
% \cventry{2019-}{Therealantidepp}{Open Source}{Malmö}{}{Help people to avoid depression. Java 11 (HttpClient), Spring boot, Hibernate, RESTful API/JSON, Swagger. }

% \cventry{2017-2018}{Fullstack Developer }{@ Verisure}{Malmö}{}{Java8, android, Docker/Kubernetes, wildfly, maven, jsp, javascript, jquery, bootstrap, AJAX, RESTful, mysql (Cassandra), git/gerrit, Linux/Ubuntu, IntelliJ, SonaQube, Nexus, Jenkins CI, Artifactory.}
% \begin{itemize}
%     \item Setup of Microservice deployment to kobol/galactica in kubernetes, myhotel 
%     \item Android development for ipcaminit   
%     \item Hands-on development in the GWIT/Installer Solutions, Fullstack – from db to javascript 
%     \item GDPR coordinator
%     Responsible for analyzing the data passing trough an application and how it relates to General Data Protection Regulation, communication with Legal, Projects and Managers. 
% \end{itemize}

% \cventry{HT2016 }{Community services in Stockholm}{@ SL}{}{}{Participated in the project responsible for improving processes around CM. Developing and maintaining a system in Java for sick travels. GitLab, Sonatype, Nexus, Maven, Git, JEE, Jenkins CI. }  
% \cventry{2014--2015}{Java developer - Java EE, Spring, Maven, Hibernate and Linux Ubuntu.}{@ Norwegian fur retailer}{}{}{Bouvet maintains an auction web-site for a Norwegian retailer of fur materials, based on JEE, hibernate, java6. I have worked to support this the site, trouble shoot, fix bugs etc. One part has been to migrate from Redhat to Scientific Linux. }  
% \cventry{2011--}{Solution Architect}{@ IKEA IT}{Helsingborg}{}{Evaluated SaaS (Software-as-a-Service, cloud computing) for a custom support system to be presented to the enterprise architecture board (EAB). The report took into account aspects such as integration issues, security, capacity, economy, legality etc.}  
% \cventry{2011--}{System Integration Specialist – TIBCO - Application Lead}{@ Hi3G (TRE)}{}{Stockholm}{
% Application Lead for EAI (Enterprise Application Integration) – a layer consisting of 15 adapters to systems for example Billing (Single.E.View), CRM (PeopleSoft) and so on. }
% \cventry{2008-2010}{Java Developer and Project Coordinator}{@ -IKEA IT}{HBG}{During my assignment at IKEA IT in 2008, parts of the organization were focused on achieving PCI DSS compliance, although I was not directly involved in that initiative.}{} 
% \cventry{2004--2012}{Java Developer and Integration specialist}{@ Telenor}{Oslo/Malmö}{}{Back-end and system integration developer Java EE and Tibco products. Delivering speed and  progress for the project which was six months late after schedule. CI-servers, cruise control – code coverage etc. 
% }  
% \begin{itemize}
%     \item Jira plugin developer, java, velocity. 
%     \item Process Designer for BPM-systems 
%     \item Defining a template for Software Architectural Description after read-in on Togaf, Zachman, Krutchen4+1, and SEI’s views and beyond. 
%     \item  System integrator tester, on site in Norway, making the final integration tests for a large BPM system that was later prized with the silver medal in BPM global Awards. Webservices, JMS, Tibo Inconcert, Integration Manager. 
%     \item Java Developer, IKEA IT 
%     \item Test Leader for J2EE project, Sony Ericsson 
%     \item Project Coordinator, IKEA IT 
% \end{itemize}

% \cventry{ 2003--2004 }{research engineer}{@ Ecole des Mines}{Nantes/France}{}{desc}  
% \begin{itemize}
%  \item As part of the research project EASYCOMP integrated Vienna component framework with the cutting edge framework for Event-based Aspect-Oriented Programming, by effectively communication with researchers in Vienna. Used java and rmi. 

%  \item Software Developer/Java for a digital library project. Analysis and design in UML and coding using J2EE, Struts, Mysql] 
% \end{itemize}
