
\large
\section {Project Mgmt, Scrum master etc}
\cventry
  {Maj 2025–}
  {Driving force in Wellness Startup project + HRV}
  {@ RMTS for Depression, Malmö}
  {} % empty date/location row
  {}
  {Help patients manage stress and wellness to relieve anxiety, depression, chronic stress, and insomnia. 
  Expert on HRV, VNS and signal processing (DFT, FFT, Arduino, DAC). Agile project management using Kanban and Trello.}

\cventry
   {2020–2025}
  {Trauma-Informed Group Facilitator, ACOA}
  {@ Online (Zoom)}
  {}
  {}
  {Facilitated Zoom-based peer-support meetings for Adult Children of Alcoholics (ACOA), using trauma-informed leadership rooted in principles from Internal Family Systems (IFS) and Nonviolent Communication (NVC). Held space for vulnerable sharing, emotional regulation, and mutual trust. Responsibilities included timekeeping, check-ins ("presentation and how do you feel"), group decision-making (group conscience), and facilitation of structured material such as *The Red Book* and *The Loving Parent Guidebook*. Developed transferable skills in psychological safety, presence-based leadership, and deep listening — directly applicable to Scrum Master and project leadership roles in high-trust IT environments.}

\cventry
  {2017–2018}
  {Sub Project Manager, GDPR Compliance}
  {@ Verisure}
  {}
  {}
  {Managed a GDPR compliance sub-project focused on internal employee-facing applications. Coordinated cross-functional efforts to ensure data privacy, consent handling, and secure processing of personal information. Worked closely with legal, IT, and product teams to align backend systems with new regulatory requirements. Delivered updated app modules supporting data subject rights and transparency in line with GDPR.}

% \cventry{2015-2016}{Problem Manager}{@ Länsstyrelsernas IT-enhet}{}{}{ITIL, problem process, incident management, service management, cross-functional teams, root cause 
% }  

% In the role as Problem Manager within Länsstyrelsernas IT-enhet, via Västra Götalands region I have driven, and coordinated meetings to solve problems spanning over different departments. Daily contact with incident managers, the coordinator for service desk, service managers for areas such as Webb, Network, Print, Hardware, Gis, Windows, Integration and message technology. Identifying bottlenecks in groups, and roles and escalating to process owner and senior management. Successfully implemented a new architecture together with an architect in one area which decreased monthly error codes from 1400 to 50.  

% \cventry{2014-2015}{Senior Project Manager / Scrum Master}{@ Nordea}{Cph/Denmark}{}{Several roles, Scrum, DevOps, Java }  
% In the role as DevOps Coach / Scrum master I have introduced agile/scrum methodologies and tools (git, jira, confluence) for a cross-functional team consisting of Operation Specialist, Automic specialists and Developers to setup test environments (preprod/uat), deployment, alarms and monitoring solutions. 

% Facilitated Scrum artefacts such as: 
% \begin{itemize}
%     \item Sprint planning meetings 
%     \item Sprint Demo 
%     \item Retrospective 
%     \item Individual coaching sessions 
% \end{itemize}

% In the role as Senior Project Manager I’ve been driving different infrastructure projects around IaaS/Amazon EC2 PoC: 
% \begin{itemize}
%     \item Project planning and documentation 
%     \item Setting up QRA – risk analysis  
%     \item Started a cross organizational local group for puppet automation, to share knowledge.
%     \item Contact with vendors, AWS and Tibco for Staffing and advise 
%     \item Initial architecture for grid solution based on Tibco DataSynapse, and Amazon EC2 for a computing grid in the cload. 
%     \item Hands-on java coding to interface to an integration motor, to provide a framework for an improved deployment solution. Springboot, maven3,  
% \end{itemize}


% \cventry{2012-2014 }{DevOps, Automatic Deployment, Knowledge Transfer, Release Management }{@ IKANO Bank}{}{}{desc}  
% \begin{itemize}
%     \item I was responsible and secured the deployment of ikanobank.se. One part of the project was to faciliate a knowledge-transfer from Germany to Denmark. At the same time I took several initatiatives necessary to create a succesful environment to deploy in, both technical-wise and process-wise. 
    
%     \item The continuous improvements, knowledge-transfer, documentation clean-up, retrospectives, coaching of ops team in agile methods and introduction of ways of working with a DevOps/C.D. Tool, CA Lisa resulted in decreased resources by about 75\% and improved quality multiple times. Handling and took initiatives to several sub-projects. 
    
%     \item Technology stack: MS .NET, BizTalk, CA Lisa/Nolio, Jenkins, Infrastructure, Load balancing, SCOM etc. Led a team of operations specialist and coordinated work between 15 people including developers, testers, etc. 
    
%     \item Work in Germany, Denmark and Sweden. 
% \end{itemize}
\cventry{2014--2015}{Senior Project Manager \& Scrum Master}{Nordea}{Copenhagen}{Scrum, DevOps, Java}{
\textbf{DevOps Coach:} Introduced agile methods (Scrum, Kanban), Git, Jira, and Confluence in a cross-functional team (Operations, Automic, Development). \\
\textbf{Scrum Facilitation:} Led sprint planning, demos, retrospectives, and coaching sessions. \\
\textbf{Infrastructure Projects:} Managed IaaS/Amazon EC2 PoC, performed risk analysis (QRA), initiated Puppet automation group. \\
\textbf{Architecture \& Coding:} Designed grid solution with Tibco DataSynapse and EC2; developed Spring Boot-based deployment integration prototype.
}

\cventry{2012--2014}{DevOps Lead \& Release Manager}{IKANO Bank}{}{.NET, BizTalk, Jenkins, Nolio}{
Led deployment of \texttt{ikanobank.se}, bridging technical and process needs. \\
Facilitated knowledge transfer from Germany to Denmark and introduced automated deployment via CA Lisa/Nolio. \\
Improved quality and efficiency through documentation cleanup, agile coaching, retrospectives, and team coordination (15+ people). \\
Worked across Sweden, Denmark, and Germany.
}

\cventry
  {2008–2009}
  {Project Coordinator, Custom Worktop Rollout}
  {@ IKEA IT}
  {}
  {}
  {Coordinated the rollout of a customized IT support system for made-to-measure kitchen worktops across multiple countries. Managed requirements gathering, project timelines, acceptance testing, and user onboarding. Bridged central IT systems with in-store operations for smooth implementation.}

\cventry
  {2005–2007}
  {Test Manager, R2R Program (Sony Ericsson)}
  {@ Sony}
  {}
  {}
  {Led the test efforts for two sub-projects within the global Record-to-Report (R2R) transformation program. Responsible for test strategy, planning, test cases, and defect management. Worked cross-functionally with development and business teams to ensure quality in financial processes and reporting systems.}

