\section*{Professional Summary}
Experienced backend developer and system integrator with a Master’s in Computer Science and Engineering and over 15 years of experience delivering complex solutions for organizations such as IKEA IT, Nordea, Telenor, Länsstyrelsen IT, Tre (Hi3G), and École des Mines de Nantes. Strong foundation in Java and J2EE, particularly from work in the Obasco team (Objects, Aspects, Components) at École des Mines de Nantes, where I contributed to advanced component-based and aspect-oriented systems.

Throughout my career, I have delivered secure, maintainable, and scalable systems across both private and public sectors, often in complex enterprise environments. My technical experience includes Java, J2EE (Learning Tree), Tibco, Microsoft BizTalk, and full-stack exposure through projects like the Udacity Nanodegree in React. I also hold a Nanodegree in Ethical Hacking from Udacity, reflecting my interest in cybersecurity and robust system design.

While my background includes senior roles and technical leadership, I am currently open to hands-on engineering roles where I can contribute directly to building stable and high-quality systems. I enjoy solving real-world problems through clean code and thoughtful architecture.

Certified in Microsoft Azure Fundamentals (AZ-900), ISTQB, and Scrum Master. Experienced with DevOps and CI/CD tools such as Docker, Kubernetes, GitHub Actions, PowerShell, and Azure CLI.

Fluent in Swedish, English, and French (C1). Based in Malmö and fully remote-ready, with flexibility to travel as needed.

