\documentclass[a4paper,11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel} % eftersom brevet är på engelska
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\usepackage{parskip}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\signature{Rickard Åberg}
\address{Bodekullsgatan 34b\\214 40 Malmö\\\\rickard.aaberg@icloud.com\\+46 709 43 14 01}
\date{\today}

\begin{document}

\begin{letter}{Manpower AB\\Malmö, Sweden}

\opening{Dear Felicia Ahlin,}

I am excited to apply for the role of IT Support Technician at Manpower. The position combines exactly what motivates me most: providing excellent service while working hands-on with IT. I am eager to contribute both my technical skills and my ability to make users feel supported and confident in their daily work.

I have a background in IT installation, troubleshooting, and support, including experience with Windows environments, Microsoft 365, and hardware such as computers, printers, and networks. I enjoy problem-solving, documenting solutions, and ensuring smooth workflows for end users. My technical curiosity keeps me motivated to learn continuously and adapt to new systems quickly.

Alongside my technical abilities, I bring strong service experience and social skills from working in people-oriented environments. I know the importance of listening carefully, responding with patience, and building trust — qualities that I believe are essential in a servicedesk role.

I am confident that my combination of technical interest, service mindset, and local knowledge of Skåne will make me a valuable asset to your team. I would welcome the opportunity to discuss how I can contribute to Manpower and your customers’ success.

\closing{Kind regards,}

\end{letter}

\end{document}
